Inefficient Concessions and Mediation

### 2021-02-03 draft.tex
integrate written notes into notes.tex and shorted proof of Lemma 3

	\frac{W}{T+D} \geq \frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
	+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} \\
	= \frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 

@@

Canceling the first two terms as well as the third and last terms, we have
	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
Expanding and canceling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have

>>>>

	\frac{W}{T+D} \geq %\frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
	%+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = \\
	\frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 

@@

Canceling the first two terms as well as the third and last terms and then 
%	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
%	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 %T\right)}
expanding and canceling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have

### 2021-02-03 notes.tex
integrate written notes into notes.tex and shorted proof of Lemma 3

\subsubsection{Solve for g}			
			First solve for $g$ starting from Expression~\ref{eq:split}:
					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
					$$pg - pge - eg \left( T - \de T + W \right)\geq \left(1 - \de \right) \left( T + D \right)$$
					\begin{equation}
						g \left(p - e \left( p + T - \de T + W \right) \right) \geq \left(1 - \de \right) \left( T + D \right)
						\label{eq:g1}
					\end{equation}
					\begin{equation}
						g_M \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}
						\label{eq:g2}
					\end{equation}
						\begin{itemize}
							\item THIS ASSUMES {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
								\begin{itemize}
									\item Note that if we set $e=0$, this is a very simple constraint on $g$
										\begin{equation}
											g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p}
											\label{eq:g3}
										\end{equation}
								\end{itemize}
							\item $T+D$, $1 - \de $ non-negative by assumption $\Rightarrow$ RHS of Expression~\ref{eq:g1} non-negative
								\begin{itemize}
									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$. AGAIN WITH THE NEGATIVE GIFTS.
								\end{itemize}
							\item To compare to the optimal gift size in the other sections:
								\begin{itemize}
									\item In Section 3 (Concessions Separating Equilibrium): $p\left(T+D\right)$
									\item Material value with $e=0$ same as in Section 3: $p\left(T+D\right)$
									\item Material value with $e=1$:
										\begin{equation}
											g^1 \geq \frac{p(1-\de_l)(T + D)}{\left(1-\de_l \right) -p(1-\de_l)T +(1-p)D}
											\label{eq:g4}
										\end{equation}
									\item Under the assumption that payoffs are multiplied by something linear like $1 + \al_2 g_1$, there's no reason to choose any intermediate value of $e$. The mediator, of course, can specify an intermediate value.
									\item We can simplify to see that the minimum gift when $e=1$ is larger when
										\[
											(1-\de)pT > (1-p)D
										\]
										\color{red} BIG NEW NOTE: This condition only true if denominator above is positive
								\end{itemize}
						\end{itemize}

@@

\subsubsection{Welfare under Mediator vs. e=0}
\label{sec:WM0}
Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\

@@

I've used Mathematica to find a parameterization under which this is true.
\begin{itemize}
	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''. Here is the constraint on $\de_h$:
		\[
		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
		\]
It turns out that there aren't really separate conditions. If the welfare under the mediator asymptotes to positive infinity to the left of the asymptote (i.e. where the gift is positive), then the mediator is better than any CSE.
					\item I've given up on deriving an analytical expression for when the mediator enhances welfare (see Mathematica programs for more detail)
					\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition
								\begin{itemize}
									\item First, note that it is not possible to have the $e$ asymptote be negative (in which case mediator can't ever work). The asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
										\[
											\frac{e p T}{1 - \de_h} > 1
										\]
										\begin{itemize}
											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
										\end{itemize}
								\end{itemize}
\end{itemize}

>>>>

\subsubsection{Solve for g}			
			First solve for $g$ starting from Expression~\ref{eq:split}:
					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
					$$pg - pge - eg \left( T - \de T + W \right)\geq \left(1 - \de \right) \left( T + D \right)$$
					\begin{equation}
						g \left(p - e \left( p + T - \de T + W \right) \right) \geq \left(1 - \de \right) \left( T + D \right)
						\label{eq:g1}
					\end{equation}
					\begin{equation}
						g_M \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}
						\label{eq:g2}
					\end{equation}
						\begin{itemize}
							\item $T+D$, $1 - \de $ non-negative by assumption $\Rightarrow$ RHS of Expression~\ref{eq:g1} non-negative
								\begin{itemize}
									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$.
									\item SO WE MUST ASSUME {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
								\end{itemize}
							\item In the complicated environment of the mechanism, I haven't actually shown that the minimum low type IC gift is optimal
							\item To compare to the optimal gift size in the other sections:
								\begin{itemize}
									\item In Section 3 (Concessions Separating Equilibrium): $p\left(T+D\right)$
									\item Material value with $e=0$ same as in Section 3: $p\left(T+D\right)$
									\item Material value with $e=1$:
										\begin{equation}
											g^1 \geq \frac{p(1-\de_l)(T + D)}{\left(1-\de_l \right) -p(1-\de_l)T +(1-p)D}
											\label{eq:g4}
										\end{equation}
									\item Under the assumption that payoffs are multiplied by something linear like $1 + \al_2 g_1$, there's no reason to choose any intermediate value of $e$. The mediator, of course, can specify an intermediate value.
									\item We can simplify to see that the minimum gift when $e=1$ is larger when
										\[
											(1-\de)pT > (1-p)D
										\]
										\color{red} BIG NEW NOTE: This condition only true if denominator above is positive
								\end{itemize}
						\end{itemize}

@@

\subsubsection{High type incentive constraint}
\begin{equation}
	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h 
	%\label{eq:med4}
\end{equation}
Turns out to be same as high type individual rationality constraint.\\

If a high type lies, there would be at least one low type, and thus no gifts and they would fight forever. So there's no investment choice for high type who lies.
\begin{itemize}
	\item This is all in the paper now.
\end{itemize}

How to choose the optimal $e$ when both the low type and high type IC bind is still done informally in R.

\subsubsection{Welfare under Mediator vs. CSE with inefficient gifts}
\label{sec:WM0}
I tried to derive a necessary condition relating the IC/IR constraints to this welfare comparison but didn't find anything easily. I think I explored this in Mathematica, but I'd need to look more carefully through the Mathematica files.

Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\

@@

I've used Mathematica to find a parameterization under which this is true.
\begin{itemize}
	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''. Here is the constraint on $\de_h$:
		\[
		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
		\]
It turns out that there aren't really separate conditions. If the welfare under the mediator asymptotes to positive infinity to the left of the asymptote (i.e. where the gift is positive), then the mediator is better than any CSE.
					\item I've given up on deriving an analytical expression for when the mediator enhances welfare (see Mathematica programs for more detail)
					\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition
								\begin{itemize}
									\item First, note that it is not possible to have the $e$ asymptote be negative (in which case mediator can't ever work). The asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
										\[
											\frac{e p T}{1 - \de_h} > 1
										\]
										\begin{itemize}
											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
												\begin{itemize}
													\item This makes welfare increasing in the gift, holding everything else constant, WHEN GIFT IS SET TO BE MINIMUM LOW-TYPE GIFT. I haven't show that's the optimal thing to do.
												\end{itemize}
											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
										\end{itemize}
								\end{itemize}
\end{itemize}
